Access channel requirements
The buzz space should not only be accessible via desktop/laptop based web browsers, but also mobile devices.

Mobile devices include, but are not restricted to cell phones and tablets. In general mobile devices refers to devices with a fairly smaller screen than a laptop or PC, but can also be carried around with ease. 

Mobile devices allow users to contribute and collaborate on the buzz spaces wherever they go. In order to ensure ease of use for mobile users, the site should adapt accordingly.

Rendering of a mobile version of the website should thus be required in order to maximise ease of use for mobile users. Since a mobile app will not be developed, mobile sites should be of high importance when designing the website. The mobile websites does not need to be an entire different site, such as a .mobi website, where the main website would be for example .co.za. The need for a responsive website therefore arises.
 
The main website should cater for large screen sizes (PC and laptops), medium screen sizes (tablets) and smaller screen sizes (mobile phones.) This can be achieved by making use of 3 different breakpoints as well as media-queries. The different breakpoints will then ensure that the page is rendered differently according to the various screen sizes. 

The website should also ensure maximum utilisation of enabled technologies on mobile devices. If it is assumed that most of the users will have smartphones, this will however not be an issue, as most smartphone devices support JavaScript, CSS3 and HTML 5, as these are the main components of a modern responsive website. If the cell phone of the client does however not support JavaScript, a website without certain client side functionality should be rendered.

The site should however also be accessible via different systems, not only accessed by users and their web browser enabled devices. It should also be able to integrate the website into other existing systems. This should be enabled by making use of iframes, but this is not recommended due to safety issues. The site should therefore be accessible by making use of hyperlinks to reach the entry point of the buzz spaces.
