%\documentclass[a4paper,12pt]{report}
%\addtolength{\textwidth}{2cm}
%\addtolength{\topmargin}{-2cm}
%\addtolength{\textheight}{3.5cm}
%\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

%\begin{document}

Performance is one of the most important quality requirements that must be fully incorporated into the system.  This includes real time access; students will be reluctant to use a system with frequent delays. Asynchronous processing will increase the systems performance, so will data partitioning, resources pooling and others specified above.  Performance is closely related to scalability, so these tactics will also enhance scalability, while ensuring good performance from a user point of view. Scalability will ensure that performance on the client side is up to standard.\\
	
Maintenance becomes easy if you design for maintainability from the outset, and be agile.
Coding readable code that is easy to understand reduces documentation, of which is ideal, but unfortunately documentation is still required.\\
 	
Systems that are available, reliable and secure encourage frequent usage.
Students study or work all day, and mostly at night, so access will be available at all times. As much as security is a top priority, access to the system should be short and one-time sign-in’s should be made possible, but in the background intense security measures, per single login attempt, can take place, e.g. input validation, authentication, and encryption.\\

It is also ideal to have small tests, to test each individual component or functionality, so as to make it easy to trace errors. If no errors were found, the big tests can be done. Testing is for developers but usability is strictly about the user point of view, so the systems must be easy to use, easy to remember how to use, as these mentioned practises will encourage users to use the system again.\\

%\end{document}